Untitled

### 2021-11-26 Main_Figures/Graphical_abstract_trait_spectra.Rmd

    plot <- plot + geom_point(data=dat, aes(x, y),size=2.5, color="azure4")

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .7 * mult * (get(x)),
                      v2 = .7 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=5.5, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))

@@

  plot <- plot + theme_ms() +ylim(-3.5,3) + xlim(-3.5,3) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("") +theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),legend.position="none",
          panel.background=element_blank(),panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),plot.background=element_blank())

>>>>

    plot <- plot + geom_point(data=dat, aes(x, y),size=3, color="grey69")

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .7 * mult * (get(x)),
                      v2 = .7 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=5.5, arrow=arrow(length=unit(0.5,"cm")), alpha=0.5, colour=c("#74c365"))

@@

  plot <- plot + theme_ms() +ylim(-3.5,3) + xlim(-3.5,3) +  theme(legend.position = c(0.095, 0.11)) +ggtitle("") +theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),legend.position="none",
          panel.background=element_blank(),panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),plot.background=element_blank(), panel.border = element_blank()
)
